A Case Study in Preserving a High Energy Physics Application

### 2014-02-27 paper.tex
modify the format of path and code

Implicit dependencies include indirect software
dependencies which is necessary for the successful execution of direct software
dependencies and other implicit dependencies. For example, we know Git is one
direct software dependency from the analysis program, which further depends on
perl, python, rsync, openssh-clients and other packages. The analysis program
accesses one file called File1, which is one symbolic link file further referring to
another file named File2.
The implicit dependencies also refers to some files under /pscratch, which is a local mount point of one PanFS with the size of 206TB.
And more importantly, the successful execution of this program greatly depends on the underlying OS and hardware platform.

@@

Even if the orginal data size referred by the program is astonishing, the size
of really used data and software is greatly smaller.
Figure~\ref{fig:data-code-size} illustrates the inputs of the tau roast program.
After the TauAnalysis procedure, the data size of Ntuples is 43.3GB, however, the atual size of really used
data in the program is 20GB.  The same trend occurs to the size of software and
other dependencies. The size of CMSSW repository is 1.16TB, the size of
packages checked out from CMSSW is 449MB, and the size of actually used CMSSW
files is only 5.2MB. 
The total size of PanFS mounted as /pscratch is 206TB, however, the really used data from /pscratch is only 119MB.
We compared the original size and actually used size of data and software in Table~\ref{table:size-original-real}.

@@

\begin{table}
    \centering
    \begin{tabular}{|l|}
        \hline
        {\bf Version 1: Email}\\ \hline
        1. Create a CMS release,\\
            \hspace{9pt} e.g. {\tt cmsrel CMSSW\_5\_3\_11\_patch3} \\
        2. Install the BEAN packages as the instructions: \\
            \hspace{9pt} {\tt https://github.com/cms-ttH/BEAN/blob/...}\\
        3. Install grid-control: \\ 
            \hspace{9pt} {\tt svn co https://ekptrac.physik.uni-ka/...} \\
        4. INstall the TauAnalysis package: \\
           \hspace{9pt} {\tt git clone https://github.com/matz-e/...} \\
           \hspace{9pt} {\tt scram b -j32} \\
        5. Fix grid\_control.cfg and run it. \\
        6. Perform the actual tau roast program. \\ 
        \hline
        {\bf Version 2: Script}\\ \hline
        {\tt set CMSSW\_BASE = (CMSSW\_5\_3\_11\_patch3)} \\
        {\tt cmsrel \$HOME/\$CMSSW\_BASE} \\
        {\tt cvs co -r V03-09-23 PhysicsTools/PatUtils} \\
        {\tt git clone {\tt https://github.com/cms-ttH/BEAN.git}} \\
        {\tt wget -r http://nd.edu/~abrinke1/ElectronEffectiveArea.h} \\
        {\tt scram b -j32} \\
        {\tt wget http://pyyaml.org/download/pyyaml/PyYAML...}\\
        \#the experiment data is from HDFS \\
        {\tt cd \$HOME/\$CMSSW\_BASE/src/PyYAML-3.10}\\
        {\tt cmsenv}\\
        {\tt python setup.py install --user} \\
        {\tt scripts/roaster data/generic\_ttl.yaml} \\ 
        \hline
        {\bf version 3: Formulated Script} \\ \hline
        set CMSSW\_BASE = (CMSSW\_5\_3\_11\_patch3) \\
        set {\bf GIT} = (https://github.com) \\
        set {\bf PYYAML} = (http://pyyaml.org) \\
        set {\bf ND} = (http://nd.edu) \\
        cmsrel \$HOME/\$CMSSW\_BASE \\
        cvs co -r V03-09-23 PhysicsTools/PatUtils \\
        git clone \${\bf GIT}/cms-ttH/BEAN.git \\
        wget -r \${\bf ND}/~abrinke1/ElectronEffectiveArea.h \\
        scram b -j32 \\
        wget \${\bf PYYAML}/download/pyyaml/PyYAML...\\
        \#the experiment data is from HDFS \\
        cd \$HOME/\$CMSSW\_BASE/src/PyYAML-3.10\\
        cmsenv\\
        python setup.py install --user \\
        scripts/roaster data/generic\_ttl.yaml \\ 
        \hline
        {\bf Version 4: Fine-Grained Toolkit}\\ \hline
        set CMSSW\_BASE = (CMSSW\_5\_3\_11\_patch3) \\
        set {\bf GIT} = (https://github.com) \\
        set {\bf PYYAML} = (http://pyyaml.org) \\
        set {\bf ND} = (http://nd.edu) \\
        cmsrel \$HOME/\$CMSSW\_BASE \\
        cvs co -r V03-09-23 PhysicsTools/PatUtils \\
        git clone \${\bf GIT}/cms-ttH/BEAN.git \\
        wget -r \${\bf ND}/~abrinke1/ElectronEffectiveArea.h \\
        scram b -j32 \\
        wget \${\bf PYYAML}/download/pyyaml/PyYAML...\\
        \#the experiment data is from HDFS \\
        cd \$HOME/\$CMSSW\_BASE/src/PyYAML-3.10\\ 
        cmsenv\\
        python setup.py install --user \\
        scripts/roaster data/generic\_ttl.yaml \\
        \hline
    \end{tabular}
    \caption{Scripts of each Solution}
    \label{table:scripts}
\end{table}

@@

\begin{table}
    \centering
    \begin{tabular}{|l|l|}
        \hline
        Archive Path & Service Description \\ \hline
        /archive/OS/path & OS Image \\ \hline
        /archive/software/path & Common Software Library \\ \hline
        /archive/CMSSW/path & CMS Software Library \\ \hline
        /archive/git/path & Git Software Library \\ \hline
        /archive/http/path & http resources \\ \hline
        /archive/experiment/path & experiment private files \\ \hline
        /archive/grid-data/path & data from the Grid \\ \hline
    \end{tabular}
    \caption{Structure Organization of the Archive}
    \label{table:archive-map}
\end{table}

Table~\ref{table:archive-map} illustrates the structure of the remote archive.
\path{/archive/OS} includes the images of different Operating Systems.
/archive/software integrates all the commonly used software, such as git,
python, perl. The archive also organizes the data from CMSSW, Git, HTTP and the
Grid. \path{/archive/experiment} includes the all the experiments submitted into the
archive. The private files and description files of each experiment will be
organized together.

The Version 4 of Table~\ref{table:scripts} illustrates the script used in
Solution 4, which is the same as the one used in Solution 3. 
However, one map file is necessary for the relocation of the data access targets, as
show in Figure~\ref{fig:version-evolution}. 
The map file redirects the git access path into /archive/git from the original path (http://github.com) referred in the script.
This design decouples the experiment script and the actual data access targets, which minimizes the impact of the evolution of different data dependencies
and ensures the transparent access.
The modification of the archive only introduces the minimal changes of the map file.

@@

Parrot is a virtual filesystem access tool which attaching existing programs to
a variety of remote I/O systems including http, ftp, gridftp, irods, HDFS,
xrootd, grow and chirp. It traps all system calls of one program through ptrace
debugging interface, and replaces them with remote I/O operations as desired.
Through executing one program under Parrot, all the paths of files involved in
this program can be recorded.

@@

\begin{table}
    \centering
    \begin{tabular}{|l|}
        \hline
        \#description of OS version and hardware architecture \\
        \#list of indirect software dependencies \\
        \# set all environment variables\\
        set CMSSW\_BASE = (CMSSW\_5\_3\_11\_patch3) \\
        cd \$HOME/\$CMSSW\_BASE/src/PyYAML-3.10\\
        cmsenv \\
        python setup.py install --user \\
        cd \$HOME/\$CMSSW\_BASE/src/ttH/TauRoast\\
        scripts/roaster data/generic\_ttl.yaml \\
        \hline
    \end{tabular}
    \caption{Script of Fine-Grained Toolkit using Parrot}
    \label{table:parrot-script}
\end{table}

@@

The command used to generate the file name list is as follows. The `-L` parameter refers to the path of the file containing all the accessed file name of the experiment.

parrot\_run -L namelist /bin/tcsh parrot\_cms.sh

The original ouput of this command is one namelist file with the size of 5.7MB
and 128,711 lines, each of which corresponds to one one accessed file of the
program. We noticed that some items appeared multiple times. To reduce the
packaging time, de-duplication and sorting techoniques are used for the
namelist file, generating one smaller file with the size of 5.7MB and 42,385
lines.

@@

\begin{figure}
\centering
\epsfig{file=package-info.eps, height=1.2in, width=2.5in}
\caption{Package Description Infomation}
\label{fig:package-info}
\end{figure}
The command used to generate the package containing all the files of L1 is as follows. 
`package1-4.sh` is a bash script which iterates each line of L1 and
determines the behavior according to the file type (common files, directories,
linked files) and the system call type.
The package description information is shown in Figure~\ref{fig:package-info}.

parrot\_run /bin/bash package1-4.sh -L ~/namelist

%*****lack: file content + metadata; only file metadata; different process solutions
Each file inside L1 is copied into the package, the final path of the file becomes the path of the package, followed by the original file path. In this program, the path of the package is /tmp/package1-4, so the final path of one file with the original path path1 is /tmp/package1-4/path1.

@@

\begin{table}
    \centering
    \begin{tabular}{|l|l|}
    \hline
    Path used in Program & Actual Location \\ \hline
    / & /tmp/package-hep \\ \hline
    /tmp/package-hep & /tmp/package-hep \\ \hline
    /dev & /dev \\ \hline
    /misc & /misc\\ \hline
    /net & /net\\ \hline
    /proc & /proc\\ \hline
    /sys & /sys\\ \hline
    /var & /var\\ \hline
    /selinux & /selinux\\ \hline
    \end{tabular}
    \caption{Structure of Map File}
    \label{table:map-file}
\end{table}

@@

parrot\_run -m /tmp/mountlist /bin/tcsh parrot\_cms.sh

@@

The map file of one package supports pattern matching semantics,
which greatly reduces the scale of the map file and improves the efficiency of file path redirection. 
For example,
one item inside the map file is "/dir1 /package-dir1" means that the access to each file and
subdirectory under /dir1 will be redirected into /package-dir1.
If the semantics of the map file do not support pattern matching, the size of the map file will become astonishing. 
/dir1 may contain thousands of files, which will generates thousands of map items and will take more time to redirect file paths.

During the packaging process, we noticed
that it is impossible to copy the files under certain directories.
For example, during namelist acquisition process, three special files under /dev directory were recorded into the namelist: tty, null and urandom, which are used for input and output.
We tried to copy these files into the new package, but the packaging utility halted.
We also noticed that copying the files under directories like /proc is
meaningless. Because the process id of one program is random and depends on the
current allocation of process ID.

As for these two file categories, letting
the program directly utilize the files on the machine, where the new user
repeats the program, is a better choice. The semantics is implemented by
setting the target path of one file equal to the origin file path inside the
map file. For example, "/dev /dev" means that when the program needs to access
files under /dev directory, it will directly use the file under /dev, which is
independent from the namespace of the package. This semantics also makes the
reference of files outside the package possible. If the new user wants to
expand the analysis of one program to his own data with the path of /A, he can add the analysis
code into the analysis script and add one item "/A /A" into the map file.

@@

The data size of Solution 4 is shown in Table~\ref{table:datasize-3rd}. The
data categories is more complex than our imagination. Except the data stored in
Hadoop and the necessary set of software, files from /pscratch, /sbin, /lib and other
paths are also necessary for the reproduction of the program.

@@

The packaging utility checks the system call of each file within the namelist,
and maintains the minimum dataset, which makes the size of the final package 
as small as possible. The total size of Hadoop under Solution 2 is astonishing,
while the size of Hadoop under the package is decreased to 20GB. The same trend
applies to the size of CMSSW\_5\_3\_11\_patch3. Because the packaging utility
tries to construct one independent and self-contained package, necessary files
from /sbin, /lib and other directories are also copied into the package and
denoted as "Other data for Package" in Table~\ref{table:datasize-2nd3rd}.

@@

Directory is one list of files and subdirectories under it. At first, we only
copied the accessed items under one directory and ignored the unaccessed items.
However, some operations on one directory depends on each item under it. For
example, `ls /dirA` is one linux command to list the name of each item under
/dirA. Because the directory itself has the name list of items under it, only
the path of the directory was recorded into the namelist in the first phrase of
Solution 4. However, when we repeated the command `ls /dirA` using the preserved package, it returned NULL because none of items under it existed in
value of `ls /dirA`, the behavior of the whole program will become incorrect
and unpredictable.

To ensure the semantics of the original program, all the items under one directory must be copied
into the package. However, the
time and space overhead appears again. Currently, Solution 4 creates one item
with the same name but the size of zero for each item under /dirA. Another
solution is to introduce one database to preserve the metadata of each file and
directory.

>>>>

Implicit dependencies include indirect software
dependencies which is necessary for the successful execution of direct software
dependencies and other implicit dependencies. For example, we know Git is one
direct software dependency from the analysis program, which further depends on
perl, python, rsync, openssh-clients and other packages. The analysis program
accesses one file called File1, which is one symbolic link file further referring to
another file named File2.
The implicit dependencies also refers to some files under {\tt /pscratch}, which is a local mount point of one PanFS with the size of 206TB.
And more importantly, the successful execution of this program greatly depends on the underlying OS and hardware platform.

@@

Even if the orginal data size referred by the program is astonishing, the size
of really used data and software is greatly smaller.
Figure~\ref{fig:data-code-size} illustrates the inputs of the tau roast program.
After the TauAnalysis procedure, the data size of Ntuples is 43.3GB, however, the atual size of really used
data in the program is 20GB.  The same trend occurs to the size of software and
other dependencies. The size of CMSSW repository is 1.16TB, the size of
packages checked out from CMSSW is 449MB, and the size of actually used CMSSW
files is only 5.2MB. 
The total size of PanFS mounted as {\tt /pscratch is 206TB}, however, the really used data from {\tt /pscratch} is only 119MB.
We compared the original size and actually used size of data and software in Table~\ref{table:size-original-real}.

@@

\begin{table}
    \centering
    \begin{tabular}{|l|}
        \hline
        {\bf Version 1: Email}\\ \hline
        1. Create a CMS release,\\
            \hspace{9pt} e.g. {\tt cmsrel CMSSW\_5\_3\_11\_patch3} \\
        2. Install the BEAN packages as the instructions: \\
            \hspace{9pt} {\tt \url{https://github.com/cms-ttH/BEAN/blob/...}}\\
        3. Install grid-control: \\ 
            \hspace{9pt} {\tt svn co \url{https://ekptrac.physik.uni-ka/...}} \\
        4. INstall the TauAnalysis package: \\
           \hspace{9pt} {\tt git clone \url{https://github.com/matz-e/...}} \\
           \hspace{9pt} {\tt scram b -j32} \\
        5. Fix grid\_control.cfg and run it. \\
        6. Perform the actual tau roast program. \\ 
        \hline
        {\bf Version 2: Script}\\ \hline
        {\tt set CMSSW\_BASE = (CMSSW\_5\_3\_11\_patch3)} \\
        {\tt cmsrel \$HOME/\$CMSSW\_BASE} \\
        {\tt cvs co -r V03-09-23 PhysicsTools/PatUtils} \\
        {\tt git clone \url{https://github.com/cms-ttH/BEAN.git}} \\
        {\tt wget -r \url{http://nd.edu/~abrinke1/...}} \\
        {\tt scram b -j32} \\
        {\tt wget \url{http://pyyaml.org/download/pyyaml/PyYAML...}}\\
        \#the experiment data is from HDFS \\
        {\tt cd \$HOME/\$CMSSW\_BASE/src/PyYAML-3.10}\\
        {\tt cmsenv}\\
        {\tt python setup.py install --user} \\
        {\tt scripts/roaster data/generic\_ttl.yaml} \\ 
        \hline
        {\bf version 3: Formulated Script} \\ \hline
        {\tt set CMSSW\_BASE = (CMSSW\_5\_3\_11\_patch3)} \\
        {\tt set {\bf GIT} = (\url{https://github.com})} \\
        {\tt set {\bf PYYAML} = (\url{http://pyyaml.org})} \\
        {\tt set {\bf ND} = (\url{http://nd.edu})} \\
        {\tt cmsrel \$HOME/\$CMSSW\_BASE} \\
        {\tt cvs co -r V03-09-23 PhysicsTools/PatUtils} \\
        {\tt git clone \${\bf GIT}/cms-ttH/BEAN.git} \\
        {\tt wget -r \${\bf ND}\url{/~abrinke1/ElectronEffectiveArea.h}} \\
        {\tt scram b -j32} \\
        {\tt wget \${\bf PYYAML}/download/pyyaml/PyYAML...}\\
        \#the experiment data is from HDFS \\
        {\tt cd \$HOME/\$CMSSW\_BASE/src/PyYAML-3.10}\\
        {\tt cmsenv}\\
        {\tt python setup.py install --user} \\
        {\tt scripts/roaster data/generic\_ttl.yaml} \\ 
        \hline
       {\bf Version 4: Fine-Grained Toolkit}\\ \hline
        {\tt set CMSSW\_BASE = (CMSSW\_5\_3\_11\_patch3)} \\
        {\tt set {\bf GIT} = (\url{https://github.com})} \\
        {\tt set {\bf PYYAML} = (\url{http://pyyaml.org})} \\
        {\tt set {\bf ND} = (\url{http://nd.edu})} \\
        {\tt cmsrel \$HOME/\$CMSSW\_BASE} \\
        {\tt cvs co -r V03-09-23 PhysicsTools/PatUtils} \\
        {\tt git clone \${\bf GIT}/cms-ttH/BEAN.git} \\
        {\tt wget -r \${\bf ND}\url{/~abrinke1/ElectronEffectiveArea.h}} \\
        {\tt scram b -j32} \\
        {\tt wget \${\bf PYYAML}/download/pyyaml/PyYAML...}\\
        \#the experiment data is from HDFS \\
        {\tt cd \$HOME/\$CMSSW\_BASE/src/PyYAML-3.10}\\
        {\tt cmsenv}\\
        {\tt python setup.py install --user} \\
        {\tt scripts/roaster data/generic\_ttl.yaml} \\ 
        \hline
    \end{tabular}
    \caption{Scripts of each Solution}
    \label{table:scripts}
\end{table}

@@

\begin{table}
    \centering
    \begin{tabular}{|l|l|}
        \hline
        Archive Path & Service Description \\ \hline
        {\tt /archive/OS/path} & OS Image \\ \hline
        {\tt /archive/software/path} & Common Software Library \\ \hline
        {\tt /archive/CMSSW/path} & CMS Software Library \\ \hline
        {\tt /archive/git/path} & Git Software Library \\ \hline
        {\tt /archive/http/path} & http resources \\ \hline
        {\tt /archive/experiment/path} & experiment private files \\ \hline
        {\tt /archive/grid-data/path} & data from the Grid \\ \hline
    \end{tabular}
    \caption{Structure Organization of the Archive}
    \label{table:archive-map}
\end{table}

Table~\ref{table:archive-map} illustrates the structure of the remote archive.
{\tt /archive/OS} includes the images of different Operating Systems.
{\tt /archive/software} integrates all the commonly used software, such as git,
python, perl. The archive also organizes the data from CMSSW, Git, HTTP and the
Grid. {\tt /archive/experiment} includes the all the experiments submitted into the
archive. The private files and description files of each experiment will be
organized together.

The Version 4 of Table~\ref{table:scripts} illustrates the script used in
Solution 4, which is the same as the one used in Solution 3. 
However, one map file is necessary for the relocation of the data access targets, as
show in Figure~\ref{fig:version-evolution}. 
The map file redirects the git access path into {\tt /archive/git} from the original path (\path{http://github.com}) referred in the script.
This design decouples the experiment script and the actual data access targets, which minimizes the impact of the evolution of different data dependencies
and ensures the transparent access.
The modification of the archive only introduces the minimal changes of the map file.

@@

Parrot is a virtual filesystem access tool which attaching existing programs to
a variety of remote {\tt I/O} systems including http, ftp, gridftp, irods, HDFS,
xrootd, grow and chirp. It traps all system calls of one program through ptrace
debugging interface, and replaces them with remote {\tt I/O} operations as desired.
Through executing one program under Parrot, all the paths of files involved in
this program can be recorded.

@@

\begin{table}
    \centering
    \begin{tabular}{|l|}
        \hline
        {\tt set CMSSW\_BASE = (CMSSW\_5\_3\_11\_patch3)} \\
        {\tt cd \$HOME/\$CMSSW\_BASE/src/PyYAML-3.10}\\
        {\tt cmsenv} \\
        {\tt python setup.py install --user} \\
        {\tt cd \$HOME/\$CMSSW\_BASE/src/ttH/TauRoast}\\
        {\tt scripts/roaster data/generic\_ttl.yaml} \\
        \hline
    \end{tabular}
    \caption{Script of Fine-Grained Toolkit using Parrot}
    \label{table:parrot-script}
\end{table}

@@

The command used to generate the file name list is as follows. The {\tt -L} parameter refers to the path of the file containing all the accessed file name of the experiment.

{\tt parrot\_run -L namelist /bin/tcsh script\_v4.sh}

The original ouput of this command is one namelist file with the size of 6.6MB
and 132,058 lines, each of which corresponds to one one accessed file of the
program. We noticed that some items appeared multiple times. To reduce the
packaging time, de-duplication and sorting techoniques are used for the
namelist file, generating one smaller file with the size of 3.2MB and 67,178 lines.

@@

\begin{figure}
\centering
\epsfig{file=package-info.eps, height=1.2in, width=2.5in}
\caption{Package Description Infomation}
\label{fig:package-info}
\end{figure}
The command used to generate the package containing all the files of L1 is as follows. 
{\tt package-utility.sh} is a bash script which iterates each line of L1 and
determines the behavior according to the file type (common files, directories,
linked files) and the system call type.
The package description information is shown in Figure~\ref{fig:package-info}.

{\tt parrot\_run /bin/bash package-utility.sh -L namelist}

%*****lack: file content + metadata; only file metadata; different process
%solutions
Each file inside L1 is copied into the package, the final path of the file
becomes the path of the package, followed by the original file path. In this
program, the path of the package is {\tt /tmp/package-hep}, so the final path of one
file with the original path path1 is {\tt /tmp/package-hep/path1}.

@@

\begin{table}
    \centering
    \begin{tabular}{|l|l|}
    \hline
    Path used in Program & Actual Location \\ \hline
    {\tt /} & {\tt /tmp/package-hep} \\ \hline
    {\tt /tmp/package-hep} & {\tt /tmp/package-hep} \\ \hline
    {\tt /dev} & {\tt /dev} \\ \hline
    {\tt /misc} & {\tt /misc}\\ \hline
    {\tt /net} & {\tt /net}\\ \hline
    {\tt /proc} & {\tt /proc}\\ \hline
    {\tt /sys} & {\tt /sys}\\ \hline
    {\tt /var} & {\tt /var}\\ \hline
    {\tt /selinux} & {\tt /selinux}\\ \hline
    \end{tabular}
    \caption{Structure of Map File}
    \label{table:map-file}
\end{table}

@@

{\tt parrot\_run -m /tmp/mountlist /bin/tcsh script\_v4.sh}

@@

The map file of one package supports pattern matching semantics,
which greatly reduces the scale of the map file and improves the efficiency of file path redirection. 
For example,
one item inside the map file is {\tt /dir1 /package-dir1} means that the access to each file and
subdirectory under {\tt /dir1} will be redirected into {\tt /package-dir1}.
If the semantics of the map file do not support pattern matching, the size of the map file will become astonishing. 
{\tt /dir1} may contain thousands of files, which will generates thousands of map items and will take more time to redirect file paths.

During the packaging process, we noticed
that it is impossible to copy the files under certain directories.
For example, during namelist acquisition process, three special files under {\tt /dev} directory were recorded into the namelist: tty, null and urandom, which are used for input and output.
We tried to copy these files into the new package, but the packaging utility halted.
We also noticed that copying the files under directories like {\tt /proc} is
meaningless. Because the process id of one program is random and depends on the
current allocation of process ID.

As for these two file categories, letting
the program directly utilize the files on the machine, where the new user
repeats the program, is a better choice. The semantics is implemented by
setting the target path of one file equal to the origin file path inside the
map file. For example, {\tt /dev /dev} means that when the program needs to access
files under {\tt /dev} directory, it will directly use the file under {\tt /dev}, which is
independent from the namespace of the package. This semantics also makes the
reference of files outside the package possible. If the new user wants to
expand the analysis of one program to his own data with the path of {\tt /A}, he can add the analysis
code into the analysis script and add one item {\tt /A /A} into the map file.

@@

The data size of Solution 4 is shown in Table~\ref{table:datasize-3rd}. The
data categories is more complex than our imagination. Except the data stored in
Hadoop and the necessary set of software, files from {\tt /pscratch, /sbin, /lib} and other
paths are also necessary for the reproduction of the program.

@@

The packaging utility checks the system call of each file within the namelist,
and maintains the minimum dataset, which makes the size of the final package 
as small as possible. The total size of Hadoop under Solution 2 is astonishing,
while the size of Hadoop under the package is decreased to 20GB. The same trend
applies to the size of CMSSW\_5\_3\_11\_patch3. Because the packaging utility
tries to construct one independent and self-contained package, necessary files
from {\tt /sbin, /lib} and other directories are also copied into the package and
denoted as "Other data for Package" in Table~\ref{table:datasize-2nd3rd}.

@@

Directory is one list of files and subdirectories under it. At first, we only
copied the accessed items under one directory and ignored the unaccessed items.
However, some operations on one directory depends on each item under it. For
example, {\tt ls /dirA} is one linux command to list the name of each item under
{\tt /dirA}. Because the directory itself has the name list of items under it, only
the path of the directory was recorded into the namelist in the first phrase of
Solution 4. However, when we repeated the command {\tt ls /dirA} using the preserved package, it returned NULL because none of items under it existed in
value of {\tt ls /dirA}, the behavior of the whole program will become incorrect
and unpredictable.

To ensure the semantics of the original program, all the items under one directory must be copied
into the package. However, the
time and space overhead appears again. Currently, Solution 4 creates one item
with the same name but the size of zero for each item under {\tt /dirA}. Another
solution is to introduce one database to preserve the metadata of each file and
directory.
